### 2014-10-20 fundamentals/examples.tex
no
erasing out of date comments
filling in examples intro.

The archetypes created by user-developers and the archetypes provided in the 
\Cycamore \cite{carlsen_cycamore_2014} repository of additional modules 
together form an `ecosystem' of capabilities. Since the long term vision for 
the \Cyclus framework includes an ever-expanding ecosystem of both general and 
specialized capability extensions within that ecosytem. The early growth and 
cross-institutional contributions to this ecosystem demonstrates a significant 
acheivement by the \Cyclus framework.

@@

\subsection{Simulations}
%FCO example (will be done soon.. publishable?)
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

\TODO{discuss FCO?}

>>>>

The \Cyclus `Ecosystem' is the collection of tools, calculation libraries, 
archetypes, data, and input files intended for use with the \Cyclus simulator. 
Members of the ecosystem include:
\begin{itemize}
\item the archetypes provided in the \Cycamore \cite{carlsen_cycamore_2014} 
repository of additional modules,
\item the archetypes created by user-developers,
\item isotopic composition data,
\item historical facility deployment data,
\item the \Cyclus \gls{GUI} tools, Cycic and Cyclist,
\item and the tools in the \Cyclus toolkit.
\end{itemize}
All together, these form an `ecosystem' of capabilities. Over time, this 
ecosystem will grow as archetype-developers, kernel-developers, and 
even users contribute capabilities developed for their own needs. Indeed, the 
long-term vision for the \Cyclus framework predicts an ever-expanding ecosystem 
of both general and specialized capability extensions within that ecosytem.

Already, the ecosystem is growing. Early cross-institutional contributions to 
the ecosystem demonstrate a significant acheivement by the \Cyclus framework 
and provide hope for a community-driven development model.

@@

\subsection{Simulations}
%Inpro example (is this still running or did we deprecate it with 1.0?)

@@

### 2014-10-20 fundamentals/impl.tex
filling in examples intro.

In Cyclus, agents can transfer discrete resource objects between each other.
Cyclus supports two types of resources:

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials ``remember'' the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time.  Cyclus can currently operate in 2 decay modes with 2 other
modes likely to be added in future releases:

@@

In large simulations there may be many material objects changing frequently, on 
the day or month timescale.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in Cyclus have some special features.  Compositions in Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that don't change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new an originating compositions. The next time the originating
composition is decayed, this cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs. \TODO{do we want a diagram helping show this composition caching?}

@@

Cycamore contains a number of useful facility models that are a mere base-set.
Additional modules are needed for interesting fuel cycle simulation. However,
simple, once-through fuel cycles can be generated with Cycamore and Cyclus alone.

<diagram of a possible Cycamore-only simulation>

>>>>

In \Cyclus, agents can transfer discrete resource objects between each other.
Cyclus supports two types of resources:

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials ``remember'' the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 2 decay modes with 2 other
modes likely to be added in future releases:

@@

In large simulations there may be many material objects changing frequently, on 
the day or month timescale.
Material decay can also contribute significantly to such changes.  In order to
help avoid unnecessary runtime performance and database space impacts,
compositions in \Cyclus have some special features.  Compositions in \Cyclus are
immutable.  This immutability allows multiple material objects to all hold
references to the same composition object safely.  When operations are
performed on a material that don't change the composition, any new resulting
materials hold a reference to the same, originating composition object.
Although the decay operation generates a new, separate composition (preserving
immutability), a reference to the new composition is placed in a cache shared
by the new an originating compositions. The next time the originating
composition is decayed, this cache will be checked for a prior calculation
with the same cumulative decay time.  If one exists, the cached composition is
used.  This cache is shared by all compositions that transitively come from
the same origin.  Composition immutability in concert with decay history
caching help eliminate many redundant decay calculations in addition to
reducing the total number of composition objects.  Since each composition
object is only recorded in the database once, significant space savings also
occurs. \TODO{do we want a diagram helping show this composition caching?}

@@

\Cycamore \cite{carlsen_cycamore_2014} contains a number of useful facility, 
region, and institution archetypes. 
As future contributions are vetted, the capabilities in \Cycamore may grow. 
However, the current \Cycamore release provides only 
basic functionality, enabling simple fuel cycle analyses. 
\Cycamore is provided so that users can get started quickly with simple 
analyses.

Figure \ref{fig:cyc_sim} shows an example of a simple, once-through fuel cycle 
that can be generated with \Cycamore and \Cyclus alone.

\begin{figure}[htbp!]
\begin{center}
<diagram of a possible Cycamore-only simulation>
\end{center}
\caption{A simple once-through fuel cycle possible with only \Cycamore and 
\Cyclus.}
\label{fig:<+label+>}
\end{figure}<++>
